---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AMKAT

<!-- badges: start -->
<!-- badges: end -->

AMKAT (short for Adaptive Multivariate Kernel-based Association Test) is a flexible,  nonparametric test for joint association between a multivariate quantitative response and a high-dimensional set of features. It includes the following notable features:

* A feature selection method for filtering noise variables out of the feature set 
* A kernel-based test statistic that uses a different kernel function for each response variable, with a method for selecting each kernel function individually
* A method of adjusting for covariate effects on the response variables
* All significant computations performed using compiled C++ routines

## Installation

You can install the development version of AMKAT using the following commands in `R`:

```
install.packages("devtools")
devtools::install_github("brianpatrickneal/AMKAT")
```

## Example

Testing is straightforward using the `amkat` function. Below, we generate toy data for a set of feature variables (`x`) and for a set of response variables (`y`), as well as for a set of covariates (`w`), and test for joint association between the features and response: 

```{r example}
library(AMKAT)
set.seed(42)
n <- 20 # sample size
y <- matrix(rnorm(3 * n), nrow = n, ncol = 3) # 3 response variables
x <- matrix(rnorm(50 * n), nrow = n, ncol = 50) # 50 feature variables
w <- matrix(rnorm(2 * n), nrow = n, ncol = 2) # 2 covariates
test_results <- amkat(y, x, covariates = w)
str(test_results)
```

## Other Information

More details on the main function `amkat` can be found in its help file. Type `?AMKATpackage` for an index of the other contents in the package's namespace.